Packaging research artifacts with RO-Crate

### 2021-05-04 latex/ro-crate.tex

% Welcome to the 2000s with UNICODE fonts!
% Adapted from
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting:_An_introduction_to_the_STIX2_OpenType_fonts
\setmathfont{STIX2Math}[
Extension={.otf},
Path=./STIX2fonts/,
Scale=1]
\setmainfont{STIX2Text}[
Extension={.otf},
Path=./STIX2fonts/,
UprightFont={*-Regular},
BoldFont={*-Bold},
ItalicFont={*-Italic},
BoldItalicFont={*-BoldItalic}]
% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
Extension={.otf},
Path=./ttf-iosevka-slab-6.1.3/,
Scale=MatchLowercase,
UprightFont={*-light},
ItalicFont={*-lightitalic}
]

>>>>

% Welcome to the 2000s with UNICODE fonts!
% Adapted from
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting:_An_introduction_to_the_STIX2_OpenType_fonts
\setmathfont{STIX2Math}[
    Extension={.otf},
    Path=./STIX2fonts/,
    Scale=1
]
\setmainfont{STIX2Text}[
    Extension={.otf},
    Path=./STIX2fonts/,
    UprightFont={*-Regular},
    BoldFont={*-Bold},
    ItalicFont={*-Italic},
    BoldItalicFont={*-BoldItalic}
]
% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
    Extension={.otf},
    Path=./ttf-iosevka-slab-6.1.3/,
    Scale=MatchLowercase,
    UprightFont={*-light},
    ItalicFont={*-lightitalic}
]
